\documentclass[sigconf]{acmart}


\begin{document}
\title{Big Data Security and Privacy}

\author{Andres Castro Benavides}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{107 S. Indiana Avenue}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{43017-6221}
}
\email{acastrob@iu.edu}

\author{Uma M Kugan}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{107 S. Indiana Avenue}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{43017-6221}
}
\email{umakugan@iu.edu}
% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Uma}

\begin{abstract}
In current world, the explosion of smart devices, social media and Internet of things resulted in major reproduction of data with high speed, huge volume and different varieties. Data is one of the biggest asset of the companies and the data growing exponentially comes with the major problem: Security and Privacy. As a result, security and privacy becomes a major initiative for any organization so that it can protects its brand, avoid penalties and in some worst cases huge loss to business as well. We need to think of way to protect, utilize, and gain real-time insight from the data that organization has. This paper is going to highlight on security and privacy in Big Data and their issues and challenges. 
\end{abstract}

\keywords{Security and Privacy, Big Data Security, Big Data, i523, HID305, HID323}

\maketitle

\section{Introduction}

\subsection{What is Big Data?}

\section{Big Data Needs Big Security}
%a) what is the problem


\section{Big Data Security Challenges}
%why is big data involved ...  Use WU descrition of Big Data 


\section{Best Practices for securing Big Data}
%how can big data or analytics of big data help


\section{Present and future of Big Data Security}
%what infrastructure/programs/systems exist for this


\section{Conclusion}

\section{References}



\section{Conclusions}



\begin{acks}
The authors would like to thank Dr. Gregor von Laszewski for his support and suggestions in writing this paper.
\end{acks}
\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

\newpage

\appendix

\section{Work Breakdown}

\begin{description}

\item[Research for section Big Security and Security Challenges:] Uma Kugan.

\item[Research for section Best practices and Present and future:] Andres Castro Benavides.

\item[Editing:] Andres Castro Benavides.

\end{description}
\end{document}
